EUV_PVE

### 2014-07-23 markdowns/master.rmd
cleaned md file

```
These are the plots and relevatn statistics for the Eucalpytus tereticornis  
pot study.  6 total contatiner volumes and 'free'seedlings all grown under  
natural field conditions during the summer of 2012
```
```{r setup}
library(knitr)
opts_knit$set(root.dir = '../')
```
```

```{r loads functions packages and plot objects, echo=FALSE, include=FALSE}
#source functions, packages, anbd plot objects
source("functions and packages/startscripts.R")

```

@@

```{r root:shoot plots }
source("master_scripts/rootshoot_plotting.R")
```

>>>>

```
These are the plots and relevatn statistics for the Eucalpytus tereticornis  
pot study.  6 total contatiner volumes and 'free'seedlings all grown under  
natural field conditions during the summer of 2012
```
```{r setup}
library(knitr)
opts_knit$set(root.dir = '../')
```
```
```{r loads functions packages and plot objects, echo=FALSE, include=FALSE}
#source functions, packages, anbd plot objects
source("functions and packages/startscripts.R")
```

@@

```{r root:shoot plots }
#source("master_scripts/rootshoot_plotting.R")
```
